---
title: "Find Pubmed publications on subject"
author: "Kishan Kumar Chudasama"
date: "20 februar 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Open Libraries
```{r}
library(RISmed)
library(ggplot2)
library(tm)
```


## Set query
```{r}
query <- "(mobile AND stroke AND unit AND prehospital)"
```

## Count records
```{r}
msu_search <- EUtilsSummary(query, type="esearch",db = "pubmed",mindate=2010, maxdate=2018, retmax=500)

QueryCount(msu_search)
queryname <- QueryId(msu_search)
queryname
```
## Specification of query Criteria with minimum and maximum date of publication of Article, number
of Articles to return

```{r}
msu_records <- EUtilsGet(msu_search)
class(msu_records) 
```

##Retrieval of abstracts from PubMed
```{r}
pubmed_data <- data.frame('Title'=ArticleTitle(msu_records),'Abstract'=AbstractText(msu_records))
head(pubmed_data,2)
```

##Storage of retrieved abstract in the form of individual text document in a directory called C:/Corpus
```{r}
for (Abs in 1:82)
{
doc1 <- data.frame(pubmed_data[Abs, ])
doc2 <- file.path("c:/corpus", paste0(Abs, ".txt"))
write.table(doc1, file = doc2, sep = "", row.names = FALSE, col.names = FALSE, quote = FALSE,
append = FALSE)
}
years <- YearPubmed(msu_records)
msu_pubs_count <- as.data.frame(table(years))
summary(msu_search)
```

##Set location
```{r}
#cname <- file.path("C:", "corpus")  
#cname
#dir(cname)
```


 
## Convert to querycount per year
```{r}
total <- NULL
for (i in 2010:2018){
peryear <- EUtilsSummary("", type="esearch", db="pubmed", mindate=i, maxdate=i)
total[i] <- QueryCount(peryear)
}
```

 
## Convert to normalized data
```{r}
year <- 2010:2018
total_pubs_count<- as.data.frame(cbind(year,total[year]))
names(total_pubs_count) <- c("year","Total_publications")
names(msu_pubs_count) <-  c("year","MSU_publications")
pubs_year <-  merge(msu_pubs_count,total_pubs_count,by="year")
pubs_year$MSU_publications_normalized <-  pubs_year$MSU_publications *100000 / pubs_year$Total_publications
```


## Write table
```{r}
write.table(pubs_year,"MSU_publications_per_year.txt",quote=F,sep="\t",row.names=F)
```


## Find which journals publications come from
```{r}
journal <- MedlineTA(msu_records)
msu_journal_count <- as.data.frame(table(journal))
msu_journal_count_top25 <- msu_journal_count[order(-msu_journal_count[,2]),][1:25,]
```

## Find top 25 journals from previous list
```{r}
journal_names <- paste(msu_journal_count_top25$journal,"[jo]",sep="")
```
 

## Count publications per journal
```{r}
total_journal <- NULL
for (i in journal_names){
perjournal <- EUtilsSummary(i, type='esearch', db='pubmed',mindate=2010, maxdate=2018)
total_journal[i] <- QueryCount(perjournal)
}
```

## Combine publications and journals, normalizing happens here
```{r}
journal_msu_total <- cbind(msu_journal_count_top25,total_journal)
names(journal_msu_total) <- c("journal","MSU_publications","Total_publications")
journal_msu_total$MSU_publications_normalized <- journal_msu_total$MSU_publications / journal_msu_total$Total_publications
```
 
## Write table for journals
```{r}
write.table(journal_msu_total,"MSU_publications_per_journal.txt",quote=F,sep="\t",row.names=F)
```
 
## Sort journals, publications per year
```{r}
pubs_per_year <- read.table("MSU_publications_per_year.txt",header = T,sep="\t")
pubs_per_journal <- read.table("MSU_publications_per_journal.txt",header = T,sep="\t")
```

## Plot number of publications
```{r}
ggplot(pubs_per_year,aes(year, MSU_publications_normalized)) + geom_line (colour="orange",size=2) +
xlab("Year") +
ylab("MSU articles")+
ggtitle("MSU PubMed articles")
View(pubs_per_year)
```


## Plot number of publications per journal
```{r}
ggplot(pubs_per_journal,aes(journal, MSU_publications,fill=journal)) + geom_bar(stat="identity")+
coord_flip()+
theme(legend.position="none")
View(pubs_per_journal)
```
 
## Plot number of publications per journal - normalized
```{r}
ggplot(pubs_per_journal ,aes(journal, MSU_publications_normalized,fill=journal)) + geom_bar(stat="identity")+
coord_flip()+
theme(legend.position="none")
View(pubs_per_journal)
```
 

